---
title: "LEDD_script"
author: "Kevin"
format: html
editor: visual
---

imports and data read-in

```{r}
library(tidyverse)

#read in LEDD data
ledd_df <- read.csv("Z1XADRCNACC_LEDD.csv")

#read in subj list of interest
subj_df <- read.csv("adrcIDs_forClinVar_pull.csv")
```

remove NA from "park_med_ptid", "park_med_admin_date", "total_ledd_calc"

```{r}
ledd_df <- ledd_df %>%
  drop_na("park_med_ptid", "park_med_admin_date", "total_ledd_calc")

```

rename 'record_id', 'park_med_visitnum', "park_med_admin_date", "total_ledd_calc"

```{r}
ledd_df <- ledd_df %>%
  rename(
    Study_ID = record_id,
    ADRC_LEDD_Visit = park_med_visitnum,
    LEDD_date = park_med_admin_date,
    LEDD_calc_tot = total_ledd_calc
  )

colnames(ledd_df)

```

convert LEDD_date to date in m/d/y

```{r}
ledd_df$LEDD_date <- as.Date(ledd_df$LEDD_date, format = "%m/%d/%y")
head(ledd_df[5:10])

```

reoder IDs and visit dates by numerical + chronological order

```{r}
ledd_df <- ledd_df %>%
  arrange(Study_ID, LEDD_date) %>%  
  group_by(Study_ID) %>%
  mutate(LEDD_time_point = row_number()) %>%  
  ungroup()

tail(ledd_df[5:10])

```

subset vars of interest

```{r}

ledd_df <- ledd_df %>%
  select(Study_ID, ADRC_LEDD_Visit, LEDD_time_point, LEDD_date, LEDD_calc_tot)

str(ledd_df)

```

remove PST-IDs that will later prohibit ID merging (str IDs vs int IDs) convert IDs and ADRC visit dates from floats to ints

```{r}

ledd_df <- ledd_df %>%
  filter(!str_detect(Study_ID, "PST")) %>%
  mutate(
    Study_ID = as.integer(Study_ID),
    ADRC_LEDD_Visit = as.integer(ADRC_LEDD_Visit)
  )

str(ledd_df)
#write.csv(ledd_df, "ledd_df.csv", row.names = FALSE)

```

read in csv with subject list of interest and merge with ledd_df on Study_ID

```{r}
merged_ledd_subj <- left_join(subj_df, ledd_df, by = 'Study_ID')

str(merged_ledd_subj)
#write.csv(merged_ledd_subj, "merged_ledd_subj.csv", row.names = FALSE)

```

remove NA

```{r}
merged_ledd_subj <- merged_ledd_subj %>%
  drop_na("ADRC_LEDD_Visit")
str(merged_ledd_subj)


```

optional final export, ledd_df with only subj of interest (NA dropped)

```{r}
#write.csv(merged_ledd_subj, "merged_ledd_subj.csv", row.names = FALSE)

```
